\documentclass{../notes}
\title{How to Do Your Own Research}
\begin{document}
\maketitle

\section{Check project is alive}
\begin{itemize}
    \item Make sure that coin is listed on at least one reputable exchange other than just dexes. If just dexes then beware. 
\end{itemize}

\section{Initial research}
\subsection{Very beginning}
Check youtube, see if project sounds interesting. 

\subsection{Helpful sites}
\begin{itemize}
    \item Messari: Profile section of coin. Make sure to take note of key people involved in the project. 
    \item Binance research: more technical research: understand the core components of the project. 
    \item Icodrops: Want to compare with messari to make sure token allocation is not substantially in the addresses of owners and token unlock periods are resonable. 
\end{itemize}
Want to write down questions. Also, Messari and Binance research m ay be a bit outdated.  

\section{Primary research}
\subsection{Youtube}
Want to watch youtube interviews with founders in chronological order. During this time want to jot down answers to questions raised on Messari and Binance Research. Want to also check out Linkedin page of owners and potentially the coin's own Youtube channel. 

\subsection{Source and documentation}
Now that understand the basic components of the project, check the primary source to make sure that the facts align. Further answer questions arisen from before. 
\begin{itemize}
    \item Tokenomics
    \item Inflation
    \item ICO
    \item Consensus mechanism
    \item Mining + staking
\end{itemize}
Want to also make sure that token allocation is good. 

\section{Roadmap, Blog, News}
Usually roadmaps are vague and interviews with founders are more than enough. Want to make sure project either has a roadmap or founders aren't just there for a cash grab. Also skim through blog of project and see if there's any substantial headlines. Also check CoinTelegraph, Coin Desk, or Decrypt and see if theres anything there. If not, not a bad sign. 

\section{Whiteboard crypto}
Goal: Try and make the project look bad. Also make sure to understand what problem the coin is solving. 

\subsection{Tokenomics}
\begin{itemize}
    \item Is the coin inflationary or deflationary
    \item Airdrop, ICO, presale, etc
\end{itemize}

\subsection{Team}
\begin{itemize}
    \item People behind the project are very important. Need to do research on them. 
\end{itemize}

\subsection{Social Media}
\begin{itemize}
    \item Check to see if there's niche Youtube channels covering just that coin. (ie Tesla daily). 
\end{itemize}
