\documentclass{../notes}
\title{Multicoin 2022 Crypto Theses}
\begin{document}
\maketitle

\section{Theses driven approach}
\begin{itemize}
    \item Make sure to have full conviction of theses
        \begin{itemize}
            \item Gather all the information
            \item Writing helps clear out holes in thought process
            \item Other people's opinion shouldn't impact thesis: only facts should influence thesis, and thus must be flexible when the facts change`
        \end{itemize}
    \item Thesis can be right but bet can be wrong. In this case, do not discard thesis, figure out why bet did not materialize. Did the facts change? 
    \item Job is not to find the best investments. Job is to become a 'truth seeker', form the best theses then find best way to expose portfolio to those theses. 
\end{itemize}

\subsection{When to sell}
\begin{enumerate}
    \item Thesis has played out and has been properly valued by the market. This is typical hedge fund approach, but Multicoin says the most profits are made at tail-end of distribution, so let the thesis actually compound. 
    \item Thesis has been invalidated by new information
    \item Like something else better
\end{enumerate}

\section{Where we are}
Still very early. Also note that high valuations compared to regular securities is that crypto is global, with \$2000 no one can buy GOOGL, but everyone can get invested in SOL, HNT, etc. 

\section{Where we are going}
Believe that in the future (5 years+) will converge to 2-3 chains: duopolies like we see in today's tech. Is it valid to compare blockchains to operating-systems in current tech? Currently is multichain. 

\section{Thinking of theses}
\begin{itemize}
    \item DEFI: global backend of financial system. Local frontends. Everyone taps in to same liquidity pool. 
    \item Metaverse: still very early. AR, render?, --backend. Same position as Eth 5 years ago 
    \item Social tokens: will redefine lots of business models in internet. Currently uses ads: terrible experience. 
    \item Excited about HNT, SOL. 
\end{itemize}
\end{document}
