\documentclass{../../notes}
\title{Valuations - DeFi}
\begin{document}
\maketitle

\section{\href{run:./understanding-defi-valuations.pdf}{Understanding DeFi valuations}}
\begin{itemize}
    \item DeFi tokens extract value at protocol value: can value as capital assets: can use traditional valuation methods: (1) Discounted Cash Flow, (2) Comparabale Company Analysis, (3) Comparable Transactions
    \item \href{https://www.tokenterminal.com/}{evaluation tool}
    \item Valuation mix of science and art: more of science for stable giants, more art for start-ups. 
    \item Relative valuation for DeFi is useless given rapidly changing tokenomics and different sectors. Same for fundamental analysis (high uncertainty, fundamental analysis does not make sense in this context). 
    \item Valuing DeFi tokens is an art: depends on subjective assessment of the future value of a token discounted to the present. Look at: product-market fit, team, community, token economics. 
    \item Practice artistry: fundamental analysis at this stage is unreliable, same for relative valuation. 
\end{itemize}

\section{\href{run:./defi-metrics-that-matter-for-a-price-recovery--fundamental-analysis.pdf}{DeFi Metrics that Matter for a Price Recovery: Fundamental Analysis}}
\begin{itemize}
    \item Fundamental analysis matters and there must be value accrual to protocol and investors, but price recovery can be more dependent to correlation to Bitcoin. Look at \# active users, trading volume, TVL, interest per year on lending protocols, amount deposited and oustanding loans for lending protocols
    \item Tokens that sold down the hardest during a crash seeminly make the biggest short-term recoveries. 
    \item High correlation between price and active user growth (seen in recovery phase). Idea: portfolio in DEXs with proportions weighted by active user growth
    \item Price performance of DEX also correlated to transaction volumes
    \item During bear markets, DEXs that allow staking for portion of fees outperforms short-term (SNX, CRV, KNC, SUSHI). During bull markets there is no correlation between protocols that allow fee accural to tokenholders (or generally long term)
    \item There is no correlation between TVL growth and price performance. Reason: capital is temporary and factors such as incentives or exploits can quickly change that. 
    \item Conclusion: During bear markets fundamentals matter. 
\end{itemize}




\end{document}

